\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: Final\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

This document summarizes the contributions of each team member for the final
demonstration and documentation.  The time period of interest is the time
between Rev 0 and the Final documentation.

\section{Team Meeting Attendance}

\wss{For each team member how many team meetings have they attended over the
time period of interest.  This number should be determined from the meeting
issues in the team's repo.  The first entry in the table should be the total
number of team meetings held by the team.}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 6\\
Hamza Issa & 6\\
Gurnoor Bal & 6\\
Ahmad Hamadi & 6\\
Jared Paul & 6\\
Harrison Chiu & 6\\
\bottomrule
\end{tabular}
\end{table}

\wss{If needed, an explanation for the counts can be provided here.}

\section{Supervisor/Stakeholder Meeting Attendance}

\wss{For each team member how many supervisor/stakeholder team meetings have
they attended over the time period of interest.  This number should be determined
from the supervisor meeting issues in the team's repo.  The first entry in the
table should be the total number of supervisor and team meetings held by the
team.  If there is no supervisor, there will usually be meetings with
stakeholders (potential users) that can serve a similar purpose.}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 0\\
Hamza Issa & 0\\
Gurnoor Bal & 0\\
Ahmad Hamadi & 0\\
Jared Paul & 0\\
Harrison Chiu & 0\\
\bottomrule
\end{tabular}
\end{table}

There was no need to meet with the supervisor. Our path to completing the project is clear. We knew exactly what to do and how to do it. Any information that he may need could easily be communicated through Teams chat instead of through a scheduled meeting.

\section{Lecture Attendance}

\wss{For each team member how many lectures have they attended over the time
period of interest.  This number should be determined from the lecture issues in
the team's repo.  The first entry in the table should be the total number of
lectures since the beginning of the term.}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 0\\
Hamza Issa & 0\\
Gurnoor Bal & 0\\
Ahmad Hamadi & 0\\
Jared Paul & 0\\
Harrison Chiu & 0\\
\bottomrule
\end{tabular}
\end{table}

There was only 1 lecture during this time period. We spend our time finishing our final project and the final documentation.

\section{TA Document Discussion Attendance}

\wss{For each team member how many of the informal document discussion meetings
with the TA were attended over the time period of interest.}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 2\\
Hamza Issa & 1\\
Gurnoor Bal & 2\\
Ahmad Hamadi & 2\\
Jared Paul & 2\\
Harrison Chiu & 1\\
\bottomrule
\end{tabular}
\end{table}

The meetings were about documentation files. Some members did not attend because they were working on things other than the documentation at that time. Furthermore, it was about asking some quick questions. The answers could easily be relayed to other members who did not attend. So, not all meetings were necessary.

\section{Commits}

\wss{For each team member how many commits to the main branch have been made
over the time period of interest.  The total is the total number of commits for
the entire team since the beginning of the term.  The percentage is the
percentage of the total commits made by each team member.}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & 8 & 100\% \\
Hamza Issa & 0 & 0\%\\
Gurnoor Bal & 0 & 0\%\\
Ahmad Hamadi & 0 & 0\%\\
Jared Paul & 1 & 0\%\\
Harrison Chiu & 8 & 100\%\\
\bottomrule
\end{tabular}
\end{table}

The only commits on the Github repo so far are documentation.
Everyone worked on the documentation equally on a separate Google Docs. We forgot to do co-authors which is why the commit distribution is off.

\section{Issue Tracker}

\wss{For each team member how many issues have they authored (including open and
closed issues (O+C)) and how many have they been assigned (only counting closed
issues (C only)) over the time period of interest.}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Hamza Issa & 3 & 0\\
Gurnoor Bal & 2 & 0\\
Ahmad Hamadi & 3 & 0\\
Jared Paul & 3 & 0\\
Harrison Chiu & 3 & 0\\
\bottomrule
\end{tabular}
\end{table}

All assigned issues are still being worked on. Members are assigned issues based on the work they want to do. Members with less assigned issues have a larger responsibility over their assigned task.

\end{document}