\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: POC\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

This document summarizes the contributions of each team member up to the POC
Demo.  The time period of interest is the time between the beginning of the term
and the POC demo.

\section{Demo Plans}

\wss{What will you be demonstrating}

\section{Team Meeting Attendance}

\wss{For each team member how many team meetings have they attended over the
time period of interest.  This number should be determined from the meeting
issues in the team's repo.  The first entry in the table should be the total
number of team meetings held by the team.}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 4\\
Ahmad Hamadi & 4\\
Harrison Chiu & 4\\
Hamza Issa & 4\\
Gurnoor Bal & 4\\
Jared Paul & 4\\
\bottomrule
\end{tabular}
\end{table}

\wss{If needed, an explanation for the counts can be provided here.}

\section{Supervisor/Stakeholder Meeting Attendance}

\wss{For each team member how many supervisor/stakeholder team meetings have
they attended over the time period of interest.  This number should be determined
from the supervisor meeting issues in the team's repo.  The first entry in the
table should be the total number of supervisor and team meetings held by the
team.  If there is no supervisor, there will usually be meetings with
stakeholders (potential users) that can serve a similar purpose.}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 2\\
Ahmad Hamadi & 2\\
Harrison Chiu & 2\\
Hamza Issa & 2\\
Gurnoor Bal & 2\\
Jared Paul & 2\\
\bottomrule
\end{tabular}
\end{table}

\wss{If needed, an explanation for the counts can be provided here.}

\section{Lecture Attendance}

\wss{For each team member how many lectures have they attended over the time
period of interest.  This number should be determined from the lecture issues in
the team's repo.  The first entry in the table should be the total number of
lectures since the beginning of the term.}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 9\\
Ahmad Hamadi & 5\\
Harrison Chiu & 6\\
Hamza Issa & 5\\
Gurnoor Bal & 6\\
Jared Paul & 5\\
\bottomrule
\end{tabular}
\end{table}

\wss{If needed, an explanation for the lecture attendance can be provided here.}

\section{TA Document Discussion Attendance}

\wss{For each team member how many of the informal document discussion meetings
with the TA were attended over the time period of interest.}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 0\\
Ahmad Hamadi & 0\\
Harrison Chiu & 0\\
Hamza Issa & 0\\
Gurnoor Bal & 0\\
Jared Paul & 0\\
\bottomrule
\end{tabular}
\end{table}

\wss{If needed, an explanation for the attendance can be provided here.}

\section{Commits}

\wss{For each team member how many commits to the main branch have been made
over the time period of interest.  The total is the total number of commits for
the entire team since the beginning of the term.  The percentage is the
percentage of the total commits made by each team member.}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & 10 & 100\% \\
Ahmad Hamadi & 2 & 20\% \\
Harrison Chiu & 2 & 20\% \\
Hamza Issa & 2 & 20\% \\
Gurnoor Bal & 2 & 20\% \\
Jared Paul & 2 & 20\% \\
\bottomrule
\end{tabular}
\end{table}

\wss{If needed, an explanation for the counts can be provided here.  For
instance, if a team member has more commits to unmerged branches, these numbers
can be provided here.  If multiple people contribute to a commit, git allows for
multi-author commits.}

\section{Issue Tracker}

\wss{For each team member how many issues have they authored (including open and
closed issues (O+C)) and how many have they been assigned (only counting closed
issues (C only)) over the time period of interest.}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Ahmad Hamadi & 3 & 2 \\
Harrison Chiu & 3 & 2 \\
Hamza Issa & 3 & 2 \\
Gurnoor Bal & 3 & 2 \\
Jared Paul & 3 & 2 \\
\bottomrule
\end{tabular}
\end{table}

Everyone had different issues assigned and closed, but in the end it came out to everyone having the same number.

\section{CICD}

The team uses CI pipelines to check the code before being merged into the protected \verb|main| branch. 
\verb|flake8| and \verb|isort| are the two Python linters that ensure our code style follows the PEP 8 
style guide and is free of static errors. There is also the \verb|black| formatter to ensure all our code
is formatted in a readable and visually appealing manner. Another CI pipeline runs for JavaScript code.
It is composed of ESLint and Prettier to ensure that JavaScript code is formatted nicely and is free of 
static errors.


\end{document}